---
title: "Data Cleaning"
author: "Oren Ross"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r data}

Demog <- read.csv("Data/Demographics.csv")
SQS_2018 <- read.csv("Data/2018_SQS_Results.csv")
SQS_2019 <- read.csv("Data/2019_SQS_Results.csv")
NYSA_ELA_School <- read.csv("Data/School_ELA_NYSA.csv")
NYSA_MATH_School <- read.csv("Data/School_MATH_NYSA.csv")
NYSA_ELA_SES <- read.csv("Data/SES_ELA_NYSA.csv")
NYSA_MATH_SES <- read.csv("Data/SES_MATH_NYSA.csv")
School_Locations <- read.csv("Data/School_Locations.csv")
Attendance_School <- read.csv("Data/Attendance_School.csv")

```


Cleaning NYSA, Demographic, and Location data

First up, the ELA NYSA scores

```{r ELA}
# colnames(NYSA_ELA_School)

# Removing columns that are not needed, ones that are number of students that scored rather than percent
NYSA_ELA_School_1 <- NYSA_ELA_School[,-c(1, 6, 7, 9, 11, 13, 15, 17)]


NYSA_ELA_School_1 <- NYSA_ELA_School_1 %>% dplyr::rename_all(function(NYSA_ELA_School_1) paste0("ELA_", NYSA_ELA_School_1))

NYSA_ELA_School_1[,5:10] <- sapply(NYSA_ELA_School_1[,5:10],as.character)
NYSA_ELA_School_1[,5:10] <- sapply(NYSA_ELA_School_1[,5:10],as.numeric)

NYSA_ELA_School_1 <- NYSA_ELA_School_1 %>% dplyr::rename(DBN = ELA_DBN)

ELA_Years <- filter(NYSA_ELA_School_1, ELA_Grade == "All Grades")
ELA_Years <- ELA_Years[, -c(3)]

ELA18 <- filter(ELA_Years, ELA_Year == "2018")
ELA19 <- filter(ELA_Years, ELA_Year == "2019")

```

Followed by the math scores

```{r MATH}
# colnames(NYSA_MATH_School)

# Removing columns that are not needed
NYSA_MATH_School_1 <- NYSA_MATH_School[,-c(1, 6, 7, 9, 11, 13, 15, 17)]


NYSA_MATH_School_1 <- NYSA_MATH_School_1 %>% dplyr::rename_all(function(NYSA_MATH_School_1) paste0("MATH_", NYSA_MATH_School_1))

NYSA_MATH_School_1[,5:10] <- sapply(NYSA_MATH_School_1[,5:10],as.character)
NYSA_MATH_School_1[,5:10] <- sapply(NYSA_MATH_School_1[,5:10],as.numeric)

NYSA_MATH_School_1 <- NYSA_MATH_School_1 %>% dplyr::rename(DBN = MATH_DBN)

MATH_Years <- filter(NYSA_MATH_School_1, MATH_Grade == "All Grades")
MATH_Years <- MATH_Years[, -c(3)]

MATH18 <- filter(MATH_Years, MATH_Year == "2018")
MATH19 <- filter(MATH_Years, MATH_Year == "2019")
```

Now by SES

```{r ELA SES}
# colnames(NYSA_ELA_SES)

# Removing columns that are not needed
NYSA_ELA_SES_1 <- NYSA_ELA_SES[,-c(1, 7, 9, 11, 13, 15, 17)]
# colnames(NYSA_ELA_SES_1)

NYSA_ELA_SES_1 <- NYSA_ELA_SES_1 %>% dplyr::rename_all(function(NYSA_ELA_SES_1) paste0("ELA_SES_", NYSA_ELA_SES_1))

NYSA_ELA_SES_1[,6:11] <- sapply(NYSA_ELA_SES_1[,6:11],as.character)
NYSA_ELA_SES_1[,6:11] <- sapply(NYSA_ELA_SES_1[,6:11],as.numeric)

NYSA_ELA_SES_1 <- NYSA_ELA_SES_1 %>% dplyr::rename(DBN = ELA_SES_DBN)

ELA_SES_Years <- filter(NYSA_ELA_SES_1, ELA_SES_Grade == "All Grades")
ELA_SES_Years <- ELA_SES_Years[, -c(3)]
# colnames(ELA_SES_Years)


# Filtering by Econ
ELA_EconDis <- filter(ELA_SES_Years, ELA_SES_Category == "Econ Disadv")
ELA_EconDis <- ELA_EconDis %>% dplyr::rename_all(function(ELA_EconDis) paste0("ELA_EconDis_", ELA_EconDis))
ELA_EconDis <- ELA_EconDis %>% dplyr::rename(DBN = ELA_EconDis_DBN)
# colnames(ELA_EconDis)
ELA_EconDis <- ELA_EconDis[,-c(2, 4)]

ELA_NotEconDis <- filter(ELA_SES_Years, ELA_SES_Category == "Not Econ Disadv")
ELA_NotEconDis <- ELA_NotEconDis %>% dplyr::rename_all(function(ELA_NotEconDis) paste0("ELA_NotEconDis_", ELA_NotEconDis))
ELA_NotEconDis <- ELA_NotEconDis %>% dplyr::rename(DBN = ELA_NotEconDis_DBN)
# colnames(ELA_NotEconDis)
ELA_NotEconDis <- ELA_NotEconDis[,-c(2, 4)]


ELA_EconDis_18 <- filter(ELA_EconDis, ELA_EconDis_ELA_SES_Year == "2018")
ELA_NotEconDis_18 <- filter(ELA_NotEconDis, ELA_NotEconDis_ELA_SES_Year == "2018")
ELA18_SES <- dplyr::inner_join(ELA_EconDis_18, ELA_NotEconDis_18, by = "DBN")
# colnames(ELA18_SES)
ELA18_SES <- ELA18_SES[,-c(2, 9)]
# colnames(ELA18_SES)

ELA_EconDis_19 <- filter(ELA_EconDis, ELA_EconDis_ELA_SES_Year == "2019")
ELA_NotEconDis_19 <- filter(ELA_NotEconDis, ELA_NotEconDis_ELA_SES_Year == "2019")
ELA19_SES <- dplyr::inner_join(ELA_EconDis_19, ELA_NotEconDis_19, by = "DBN")
# colnames(ELA19_SES)
ELA19_SES <- ELA19_SES[,-c(2, 9)]
# colnames(ELA19_SES)


```


```{r MATH SES}
# colnames(NYSA_MATH_SES)

# Removing columns that are not needed
NYSA_MATH_SES_1 <- NYSA_MATH_SES[,-c(1, 7, 9, 11, 13, 15, 17)]
# colnames(NYSA_MATH_SES_1)

NYSA_MATH_SES_1 <- NYSA_MATH_SES_1 %>% dplyr::rename_all(function(NYSA_MATH_SES_1) paste0("MATH_SES_", NYSA_MATH_SES_1))

NYSA_MATH_SES_1[,6:11] <- sapply(NYSA_MATH_SES_1[,6:11],as.character)
NYSA_MATH_SES_1[,6:11] <- sapply(NYSA_MATH_SES_1[,6:11],as.numeric)

NYSA_MATH_SES_1 <- NYSA_MATH_SES_1 %>% dplyr::rename(DBN = MATH_SES_DBN)

MATH_SES_Years <- filter(NYSA_MATH_SES_1, MATH_SES_Grade == "All Grades")
MATH_SES_Years <- MATH_SES_Years[, -c(3)]
# colnames(MATH_SES_Years)


# Filtering by Econ
MATH_EconDis <- filter(MATH_SES_Years, MATH_SES_Category == "Econ Disadv")
MATH_EconDis <- MATH_EconDis %>% dplyr::rename_all(function(MATH_EconDis) paste0("MATH_EconDis_", MATH_EconDis))
MATH_EconDis <- MATH_EconDis %>% dplyr::rename(DBN = MATH_EconDis_DBN)
# colnames(MATH_EconDis)
MATH_EconDis <- MATH_EconDis[,-c(2, 4)]

MATH_NotEconDis <- filter(MATH_SES_Years, MATH_SES_Category == "Not Econ Disadv")
MATH_NotEconDis <- MATH_NotEconDis %>% dplyr::rename_all(function(MATH_NotEconDis) paste0("MATH_NotEconDis_", MATH_NotEconDis))
MATH_NotEconDis <- MATH_NotEconDis %>% dplyr::rename(DBN = MATH_NotEconDis_DBN)
# colnames(MATH_NotEconDis)
MATH_NotEconDis <- MATH_NotEconDis[,-c(2, 4)]


MATH_EconDis_18 <- filter(MATH_EconDis, MATH_EconDis_MATH_SES_Year == "2018")
MATH_NotEconDis_18 <- filter(MATH_NotEconDis, MATH_NotEconDis_MATH_SES_Year == "2018")
MATH18_SES <- dplyr::inner_join(MATH_EconDis_18, MATH_NotEconDis_18, by = "DBN")
# colnames(MATH18_SES)
MATH18_SES <- MATH18_SES[,-c(2, 9)]
# colnames(MATH18_SES)

MATH_EconDis_19 <- filter(MATH_EconDis, MATH_EconDis_MATH_SES_Year == "2019")
MATH_NotEconDis_19 <- filter(MATH_NotEconDis, MATH_NotEconDis_MATH_SES_Year == "2019")
MATH19_SES <- dplyr::inner_join(MATH_EconDis_19, MATH_NotEconDis_19, by = "DBN")
# colnames(MATH19_SES)
MATH19_SES <- MATH19_SES[,-c(2, 9)]
# colnames(MATH19_SES)



```

Time to merge NYSA scores

```{r merge NYSA}

ELANYSA_18 <- dplyr::inner_join(ELA18, ELA18_SES, by = "DBN")
MATHNYSA_18 <- dplyr::inner_join(MATH18, MATH18_SES, by = "DBN")
NYSA_18 <- dplyr::inner_join(ELANYSA_18, MATHNYSA_18, by = "DBN")

ELANYSA_19 <- dplyr::inner_join(ELA19, ELA19_SES, by = "DBN")
MATHNYSA_19 <- dplyr::inner_join(MATH19, MATH19_SES, by = "DBN")
NYSA_19 <- dplyr::inner_join(ELANYSA_19, MATHNYSA_19, by = "DBN")

```




```{r demographic data}

Demog$X..Female.1 <- gsub( "%", "", Demog$X..Female.1)
Demog$X..Male.1 <- gsub( "%", "", Demog$X..Male.1)
Demog$X..Asian.1 <- gsub( "%", "", Demog$X..Asian.1)
Demog$X..Black.1 <- gsub( "%", "", Demog$X..Black.1)
Demog$X..Hispanic.1 <- gsub( "%", "", Demog$X..Hispanic.1)
Demog$X..Multiple.Race.Categories.Not.Represented.1 <- gsub( "%", "", Demog$X..Multiple.Race.Categories.Not.Represented.1)
Demog$X..White.1 <- gsub( "%", "", Demog$X..White.1)
Demog$X..Students.with.Disabilities.1 <- gsub( "%", "", Demog$X..Students.with.Disabilities.1)
Demog$X..English.Language.Learners.1 <- gsub( "%", "", Demog$X..English.Language.Learners.1 )
Demog$X..Poverty.1 <- gsub( "%", "", Demog$X..Poverty.1)
Demog$Economic.Need.Index <- gsub( "%", "", Demog$Economic.Need.Index)

Demog[,12:39] <- sapply(Demog[,12:39],as.character)
Demog[,12:39] <- sapply(Demog[,12:39],as.numeric)


Demo18 <- filter(Demog, Year == "2017-18")
Demo19 <- filter(Demog, Year == "2018-19")

```



Editing the locations data so it works with what I am looking at

```{r Locations}
# Checking names of columns to see what I need to keep
# colnames(School_Locations)

# Removing unneccesesary columns
School_Locations_1 <- School_Locations[,-c(1, 3, 5:13, 21:22, 24:27, 30:33, 35:38)]

# Converting code names into charcters
School_Locations_1[,1] <- sapply(School_Locations_1[,1], as.character)

# colnames(School_Locations_1)

# Converting some intgers to factors
School_Locations_1[,7:9] <- sapply(School_Locations_1[,7:9], as.character)
School_Locations_1[,7:9] <- lapply(School_Locations_1[,7:9], factor)

# converting Coordinate to numerical
School_Locations_1[,5:6] <- sapply(School_Locations_1[,5:6],as.character)
School_Locations_1[,5:6] <- sapply(School_Locations_1[,5:6],as.numeric)

# Changing the name of column for later use
colnames(School_Locations_1)[2] <- "School.Name"
# colnames(School_Locations_1)

School_Locations_1 <- School_Locations_1 %>% separate(Location.1,
                c("Borough", "Zip", "Latitude", "Longitude"), sep = "([\\,\\(\\)])")
School_Locations_1$Zip <- gsub( "NY ", "", School_Locations_1$Zip)
School_Locations_1$Borough <- sapply(School_Locations_1$Borough, factor)
School_Locations_1$Zip <- sapply(School_Locations_1$Zip, factor)
options(digits=9)
School_Locations_1$Latitude <- sapply(School_Locations_1$Latitude, as.numeric)
School_Locations_1$Longitude <- sapply(School_Locations_1$Longitude, as.numeric)

# Something is off in boroughs
unique(School_Locations_1$Borough)

# Fixing boroughs
School_Locations_1$Borough<- gsub( "Bronx", "BRONX", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "ROCKAWAY PARK", "QUEENS", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "JAMAICA", "QUEENS", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "JACKSON HEIGHTS", "QUEENS", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "Staten Island", "STATEN ISLAND", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "NEW YORK", "MANHATTAN", School_Locations_1$Borough)
School_Locations_1$Borough <- sapply(School_Locations_1$Borough,as.factor)


School_Locations_1$Borough<- gsub( "BAYSIDE", "QUEENS", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "JAMAICA", "QUEENS", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "LONG ISLAND CITY", "QUEENS", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "IS", "ISLAND", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "ISLANDLAND", "ISLAND", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "New York", "MANHATTAN", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "MANHATTAN CITY", "MANHATTAN", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "Long Island City", "QUEENS", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "Manhattan", "MANHATTAN", School_Locations_1$Borough)
School_Locations_1$Borough<- gsub( "Brooklyn", "BROOKLYN", School_Locations_1$Borough)
School_Locations_1$Borough[1580] <- "QUEENS"


unique(School_Locations_1$Borough)

School_Locations_1 <- mutate_at(School_Locations_1, vars(Borough), as.factor)



```

Merging Demo and Location

```{r merging demo and locations}
DEMO_LOC_18 <- dplyr::inner_join(Demo18, School_Locations_1, by = "School.Name")
DEMO_LOC_19 <- dplyr::inner_join(Demo19, School_Locations_1, by = "School.Name")
```

And now merging NYSA and Demo/Loc

```{r merging scores and demo/loc}
NYSA_DEM_LOC_18 <- dplyr::inner_join(NYSA_18, DEMO_LOC_18, by = "DBN")
NYSA_DEM_LOC_19 <- dplyr::inner_join(NYSA_19, DEMO_LOC_19, by = "DBN")

# colnames(NYSA_DEM_LOC_18)
NYSA_DEM_LOC_18 <- NYSA_DEM_LOC_18[,-c(3,22, 23, 42, 43, 45:59, 61, 63, 65, 67 ,69, 71, 73, 75, 77, 80)]
# colnames(NYSA_DEM_LOC_19)
NYSA_DEM_LOC_19 <- NYSA_DEM_LOC_19[,-c(3,22, 23, 42, 43, 45:59, 61, 63, 65, 67 ,69, 71, 73, 75, 77, 80)]
```


Now I am going to clean the SQS Data

First up 2018

```{r SQS Data Clean}
# str(SQS_2018)

SQS_2018_1 <- SQS_2018

#Converting factors to numeric for DF
SQS_2018_1$Total.Parent..Response.Rate <- gsub( "%", "", SQS_2018_1$Total.Parent..Response.Rate)
SQS_2018_1$Total.Teacher.Response.Rate <- gsub( "%", "", SQS_2018_1$Total.Teacher.Response.Rate)
SQS_2018_1$Total.Student.Response.Rate <- gsub( "%", "", SQS_2018_1$Total.Student.Response.Rate)


SQS_2018_1[,3:11] <- sapply(SQS_2018_1[,3:11],as.character)
SQS_2018_1[,3:11] <- sapply(SQS_2018_1[,3:11],as.numeric)

#Calculate NAs for each column
colSums(is.na(SQS_2018_1))

```

First need to remove supportive environment score because it is all NA. Based on the data, it might be best to remove all the schools that have NA for Strong Family Community Ties, since it will most likely remove all the ones that have ANY for some of the other columns.

```{r remove rows}

SQS_2018_1 <- SQS_2018_1[,-9]


SQS_2018_1 <- SQS_2018_1[complete.cases(SQS_2018_1$Strong.Family.Community.Ties.Score),]
colSums(is.na(SQS_2018_1))

#also going to remove the last 6 rows with out the final four of the scores
SQS_2018_1 <- SQS_2018_1[complete.cases(SQS_2018_1$Rigorous.Instruction.Score),]
colSums(is.na(SQS_2018_1))

```

Now we only have the 610 students response rates that are missing. This is something we can figure out later.

NOW REPEATING FOR 2019


```{r SQS Data Clean}

SQS_2019_1 <- SQS_2019[,-c(9)]
# str(SQS_2019_1)
# colnames(SQS_2019_1)
#Converting factors to numeric for DF

colnames(SQS_2019_1)[3] <- "Total.Parent..Response.Rate"
colnames(SQS_2019_1)[4] <- "Total.Teacher.Response.Rate"
colnames(SQS_2019_1)[5] <- "Total.Student.Response.Rate"

# str(SQS_2019_1)

SQS_2019_1$Total.Parent..Response.Rate <- gsub( "%", "", SQS_2019_1$Total.Parent..Response.Rate)
SQS_2019_1$Total.Teacher.Response.Rate <- gsub( "%", "", SQS_2019_1$Total.Teacher.Response.Rate)
SQS_2019_1$Total.Student.Response.Rate <- gsub( "%", "", SQS_2019_1$Total.Student.Response.Rate)
SQS_2019_1[,4:10] <- sapply(SQS_2019_1[,4:10],as.character)
SQS_2019_1[,3:10] <- sapply(SQS_2019_1[,3:10],as.numeric)


#Calculate NAs for each column
colSums(is.na(SQS_2019_1))


```

Based on the data, it might be best to remove all the schools that have NA for Strong Family Community Ties, since it will most likely remove all the ones that have ANY for some of the other columns.

```{r remove rows}
SQS_2019_1 <- SQS_2019_1[complete.cases(SQS_2019_1$Strong.Family.Community.Ties.Score),]
colSums(is.na(SQS_2019_1))

#now removing rigourous instruction bc it should remove the rest
SQS_2019_1 <- SQS_2019_1[complete.cases(SQS_2019_1$Rigorous.Instruction.Score),]
colSums(is.na(SQS_2019_1))

```

Now we only have the 641 students response rates that are missing. This is something we can figure out later, since it is similar to the 2018

MERGING DATA TIME!!
```{r time to fully merge}
Full_18 <- dplyr::inner_join(SQS_2018_1, NYSA_DEM_LOC_18, by = "DBN")
# colnames(Full_18)
Full_18 <- Full_18[,-11]
Full_18$Year <- "2018"

Full_19 <- dplyr::inner_join(SQS_2019_1, NYSA_DEM_LOC_19, by = "DBN")
Full_19 <- Full_19[,-11]
Full_19$Year <- "2019"
# colnames(Full_19)
```


```{r joining and renaming cols}

FinalDF <- dplyr::full_join(Full_18, Full_19)


# Now time to fix column names and stuff

FinalDF$UniqueID <- paste(FinalDF$DBN, FinalDF$Year)
# colnames(FinalDF)[23] <- "ELA.NotEconDis.ELA.SES.Mean.Scale.Score"
for ( col in 1:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  sub("X..", "", colnames(FinalDF)[col])
}
for ( col in 1:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  sub(".1", "", colnames(FinalDF)[col])
}
for ( col in 1:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  sub(".3.4", ".Passing", colnames(FinalDF)[col])
}
for ( col in 1:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  gsub("[_]", ".", colnames(FinalDF)[col])
}

for ( col in 1:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  gsub(".Score", "", colnames(FinalDF)[col])
}



for ( col in 1:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  sub(".MATH", "", colnames(FinalDF)[col])
}

for ( col in 1:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  sub(".ELA", "", colnames(FinalDF)[col])
}

colnames(FinalDF)[53] <- "Multi.Racial"
colnames(FinalDF)[61] <- "X.COORDINATE"

# Rescaling

FinalDF[,76:80]<-FinalDF[,6:10]*20

for ( col in 76:ncol(FinalDF)){
    colnames(FinalDF)[col] <-  sub(".1", "_Rescaled", colnames(FinalDF)[col])
}


```



Creating Column for differences in mean by SES

```{r differences in means scores}
FinalDF$ELA.SES.Difference.Mean <- FinalDF$ELA.NotEconDis.SES.Mean.Scale - FinalDF$ELA.EconDis.SES.Mean.Scale
FinalDF$ELA.SES.Difference.Passing <- FinalDF$ELA.NotEconDis.SES.Level.Passing - FinalDF$ELA.EconDis.SES.Level.Passing

FinalDF$MATH.SES.Difference.Mean.Scores <- FinalDF$MATH.NotEconDis.SES.Mean.Scale - FinalDF$MATH.EconDis.SES.Mean.Scale
FinalDF$MATH.SES.Difference.Passing <- FinalDF$MATH.NotEconDis.SES.Level.Passing - FinalDF$MATH.EconDis.SES.Level.Passing





```


```{r}
# Now a list of all the column names to refer to later
colnames(FinalDF)

```




```{r code for cleaning tables}
Col.Labels.Clean <- c(
  `(Intercept)` = "Intercept",
  Collaborative.Teachers = "Collaborative Teachers Score",
  Effective.School.Leadership = "Effective School Leadership Score", 
  Rigorous.Instruction = "Rigorous Instruction Score", 
  Strong.Family.Community.Ties = "Strong Family Community Ties Score",
  Trust = "Trust Score",
  ELA.Mean.Scale = "ELA Mean Test Score", 
  ELA.Level.Passing = "ELA Percent Passing",
  ELA.EconDis.SES.Mean.Scale = "ELA Mean Test Score - Economically Disadvantaged",
  ELA.NotEconDis.SES.Mean.Scale = "ELA Mean Test Score - Not Economically Disadvantaged",
    ELA.EconDis.SES.Level.Passing = "ELA Mean Percent Passing - Economically Disadvantaged",
  ELA.NotEconDis.SES.Level.Passing = "ELA Mean Percent Passing - Not Economically Disadvantaged",
    MATH.Mean.Scale = "MATH Mean Test Score", 
  MATH.Level.Passing = "MATH Percent Passing",
  MATH.EconDis.SES.Mean.Scale = "MATH Mean Test Score - Economically Disadvantaged",
  MATH.NotEconDis.SES.Mean.Scale = "MATH Mean Test Score - Not Economically Disadvantaged",
    MATH.EconDis.SES.Level.Passing = "MATH Mean Percent Passing - Economically Disadvantaged",
  MATH.NotEconDis.SES.Level.Passing = "MATH Mean Percent Passing - Not Economically Disadvantaged",
  Multi.Racial = "Multi Racial",                                                   
Students.with.Disabilities =  "Students with Disabilities",   
English.Language.Learners = "English Language Learners",                    
Economic.Need.Index = "Economic Need Index",
  Collaborative.Teachers_Rescaled = "Collaborative Teachers Score (Rescaled 0-100)",
  Effective.School.Leadership_Rescaled = "Effective School Leadership Score (Rescaled 0-100)", 
  Rigorous.Instruction_Rescaled = "Rigorous Instruction Score (Rescaled 0-100)", 
  Strong.Family.Community.Ties_Rescaled = "Strong Family Community Ties Score (Rescaled 0-100)",
  Trust_Rescaled = "Trust Score (Rescaled 0-100)",
ELA.SES.Difference.Mean = "ELA Difference in Mean Score (Between Not Economically Disadvantaged and Economically Disadvantaged)"  ,            
ELA.SES.Difference.Mean = "ELA Difference in Percent Passing (Between Not Economically Disadvantaged and Economically Disadvantaged)"  ,

MATH.SES.Difference.Mean = "MATH Difference in Mean Score (Between Not Economically Disadvantaged and Economically Disadvantaged)"  ,            
MATH.SES.Difference.Mean = "MATH Difference in Percent Passing (Between Not Economically Disadvantaged and Economically Disadvantaged)" ,
  Collaborative.Teachers_Rescaled_GroupMean = "Collaborative Teachers Score - Group Mean (Rescaled 0-100)",
  Effective.School.Leadership_Rescaled_GroupMean = "Effective School Leadership Score - Group Mean (Rescaled 0-100)", 
  Rigorous.Instruction_Rescaled_GroupMean = "Rigorous Instruction Score - Group Mean (Rescaled 0-100)", 
  Strong.Family.Community.Ties_Rescaled_GroupMean = "Strong Family Community Ties Score - Group Mean (Rescaled 0-100)",
  Trust_Rescaled_GroupMean = "Trust Score - Group Mean (Rescaled 0-100)",


Multi.Racial_GroupMean = "Multi Racial - Group Mean", 
Asian_GroupMean = "Asian - Group Mean", 
Black_GroupMean = "Black - Group Mean", 
Hispanic_GroupMean = "Hispanic - Group Mean", 
White_GroupMean = "White - Group Mean", 
Multi.Racial_GroupMean = "Multi Racial - Group Mean", 
Students.with.Disabilities_GroupMean =  "Students with Disabilities - Group Mean",   
English.Language.Learners_GroupMean = "English Language Learners - Group Mean",                    
Economic.Need.Index_GroupMean = "Economic Need Index - Group Mean"

)

# Creating easy callback for SQS formulas
SQS_Rescaled <- c("Collaborative.Teachers_Rescaled", "Effective.School.Leadership_Rescaled", "Rigorous.Instruction_Rescaled", "Strong.Family.Community.Ties_Rescaled", "Trust_Rescaled")
SQS_Orig <- c("Collaborative.Teachers", "Effective.School.Leadership", "Rigorous.Instruction", "Strong.Family.Community.Ties", "Trust")

# Creating easy callback for Demographics for formulas
Race_formula <- c("Asian", "Black", "Hispanic", "Multi.Racial", "White")
Learn_Formula <- c("Students.with.Disabilities", "English.Language.Learners")

RaceENI_formula <- c("Asian", "Black", "Hispanic", "Multi.Racial", "White", "Economic.Need.Index")
# Just an example on how to create formula
# as.formula(paste("ELA.Level.Passing", paste(SQS, collapse=" + ", sep = " + "), sep=" ~ "))
# 
# paste("ELA.Level.Passing", paste(paste(SQS_Rescaled, collapse=" + ", sep = " + "), "Economic.Need.Index",  collapse=" + ", sep = " + "), sep=" ~ ") 
# 
# 
# as.formula(paste("ELA.Level.Passing", paste(paste(paste(SQS_Rescaled, collapse=" + ", sep = " + "), "Economic.Need.Index",  collapse=" + ", sep = " + "), "Economic.Need.Index|Rigorous.Instruction_Rescaled",  collapse=" + ", sep = " + "), sep=" ~ ")  )



# 
# 
# testingDF <- var_labels(FinalDF,
#   Collaborative.Teachers = "Collaborative Teachers Score",
#   Effective.School.Leadership = "Effective School Leadership Score", 
#   Rigorous.Instruction = "Rigorous Instruction Score", 
#   Strong.Family.Community.Ties = "Strong Family Community Ties Score",
#   Trust = "Trust Score",
#   ELA.Mean.Scale = "ELA Mean Test Score", 
#   ELA.Level.Passing = "ELA Percent Passing",
#   ELA.EconDis.SES.Mean.Scale = "ELA Mean Test Score - Economically Disadvantaged",
#   ELA.NotEconDis.SES.Mean.Scale = "ELA Mean Test Score - Not Economically Disadvantaged",
#     ELA.EconDis.SES.Level.Passing = "ELA Mean Percent Passing - Economically Disadvantaged",
#   ELA.NotEconDis.SES.Level.Passing = "ELA Mean Percent Passing - Not Economically Disadvantaged",
#     MATH.Mean.Scale = "MATH Mean Test Score", 
#   MATH.Level.Passing = "MATH Percent Passing",
#   MATH.EconDis.SES.Mean.Scale = "MATH Mean Test Score - Economically Disadvantaged",
#   MATH.NotEconDis.SES.Mean.Scale = "MATH Mean Test Score - Not Economically Disadvantaged",
#     MATH.EconDis.SES.Level.Passing = "MATH Mean Percent Passing - Economically Disadvantaged",
#   MATH.NotEconDis.SES.Level.Passing = "MATH Mean Percent Passing - Not Economically Disadvantaged",
#   Multi.Racial = "Multi Racial",                                                   
# Students.with.Disabilities =  "Students with Disabilities",   
# English.Language.Learners = "English Language Learners",                    
# Economic.Need.Index = "Economic Need Index",
#   Collaborative.Teachers_Rescaled = "Collaborative Teachers Score (Rescaled 0-100)",
#   Effective.School.Leadership_Rescaled = "Effective School Leadership Score (Rescaled 0-100)", 
#   Rigorous.Instruction_Rescaled = "Rigorous Instruction Score (Rescaled 0-100)", 
#   Strong.Family.Community.Ties_Rescaled = "Strong Family Community Ties Score (Rescaled 0-100)",
#   Trust_Rescaled = "Trust Score (Rescaled 0-100)"
# # ELA.SES.Difference.Mean = "ELA Difference in Mean Score (Between Not Economically Disadvantaged and Economically Disadvantaged)"  ,            
# # ELA.SES.Difference.Mean = "ELA Difference in Percent Passing (Between Not Economically Disadvantaged and Economically Disadvantaged)"  ,
# # 
# # MATH.SES.Difference.Mean = "MATH Difference in Mean Score (Between Not Economically Disadvantaged and Economically Disadvantaged)"  ,            
# # MATH.SES.Difference.Mean = "MATH Difference in Percent Passing (Between Not Economically Disadvantaged and Economically Disadvantaged)" 
# )


```

